Challenging Fuel Cycle Modeling Assumptions: Facility and Time Step Discretization Effects

### 2015-10-06 paper.tex
working on NT journal manuscript detail requirements

%%%%%% acronyms %%%%%%
\usepackage[acronym,toc]{glossaries}
\newacronym{MIT}{MIT}{the Massachusetts Institute of Technology}
\newacronym{UW}{UW}{University of Wisconsin}
%\newacronym{<++>}{<++>}{<++>}
\makeglossaries

@@

%%%%%%%% cover info %%%%%%%%%%%%%%%
\title{Facility and Time Step Discretization Effects in Fuel Cycle Simulation}
\author{Robert~W.~Carlsen, Paul~P.H.~Wilson}

@@

% No more than three keywords, though each can be a phrase
\keywords{nuclear fuel cycle, simulation, TODO:third}

@@

@@

\newpage

\begin{abstract}

Due to the diversity of fuel cycle simulator modeling assumptions, direct
comparison and benchmarking can be difficult.  In 2012 the Organisation for
Economic Co-operation and Development (OECD) completed a benchmark study that
is perhaps one of the most complete published comparisons performed.  Despite
this, however, various results from the simulators were often significantly
different due to inconsistency in modeling decisions involving reprocessing
strategies, refueling behavior, reactor end-of-life handling, etc.  This work
attempts to identify and quantify the effects of selected modeling choices
that may sometimes be taken for granted in the fuel cycle modeling domain.
Four scenarios are compared using combinations of either fleet-based or
individual reactors with either monthly or quarterly (3-month) time steps.
The Cyclus fuel cycle simulator's plug-in facility cability along with its
market-like dynamic material routing allow it to be used as a level playing
field for comparing the scenarios.  When under supply-constraint pressure, the
four cases exhibit noticably different behavior.  Fleet-based modeling is more
efficient in supply-constrained environments at the expense of losing insight
on issues such as realistically suboptimal fuel distribution and challenges in
reactor refueling cycle staggering.  Finer-grained time steps also enable more
efficient material use in supply-constrained environments.  Large simulations
with fleet-based reactors run much more quickly than their individual reactor
counterparts.

\end{abstract}

@@

\subsection{CYCLUS}

>>>>

%%%%%% acronyms %%%%%%
\usepackage[acronym,toc]{glossaries}
\newacronym{UW}{UW}{University of Wisconsin}
%\newacronym{<++>}{<++>}{<++>}
\makeglossaries

@@

%%%%%%%% cover info %%%%%%%%%%%%%%%
\title{Challenging Fuel Cycle Modeling Assumptions: Facility and Time Step Discretization Effects}
\author{Robert~W.~Carlsen, Paul~P.H.~Wilson}

@@

% No more than three keywords, though each can be a phrase
\keywords{Nuclear Fuel Cycle, Simulation, \Cyclus}

@@

\myabstract{
Due to the diversity of fuel cycle simulator modeling assumptions, direct
comparison and benchmarking can be difficult.  In 2012 the Organisation for
Economic Co-operation and Development (OECD) completed a benchmark study that
is perhaps one of the most complete published comparisons performed.  Despite
this, however, various results from the simulators were often significantly
different due to inconsistency in modeling decisions involving reprocessing
strategies, refueling behavior, reactor end-of-life handling, etc.  This work
attempts to identify and quantify the effects of selected modeling choices
that may sometimes be taken for granted in the fuel cycle modeling domain.
Four scenarios are compared using combinations of either fleet-based or
individual reactors with either monthly or quarterly (3-month) time steps.
The Cyclus fuel cycle simulator's plug-in facility cability along with its
market-like dynamic material routing allow it to be used as a level playing
field for comparing the scenarios.  When under supply-constraint pressure, the
four cases exhibit noticably different behavior.  Fleet-based modeling is more
efficient in supply-constrained environments at the expense of losing insight
on issues such as realistically suboptimal fuel distribution and challenges in
reactor refueling cycle staggering.  Finer-grained time steps also enable more
efficient material use in supply-constrained environments.  Large simulations
with fleet-based reactors run much more quickly than their individual reactor
counterparts.
}

@@

@@

\subsection{\Cyclus}
